---
title: "Analysis of Stage Shift - Mortality Correlations"
author: "James Long"
always_allow_html: yes
date: "`r Sys.Date()`"
output:
  html_document:
    theme: united
    toc: yes
    toc_collapsed: yes
    toc_float: yes
---

```{r alternative-preambles,echo=FALSE,include=FALSE,eval=FALSE}
## if using word replace output with
output:
  word_document:
    toc: yes

## if using pdf replace output with
output:
  pdf_document:
    toc: yes
header-includes:
  - \usepackage{xcolor}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

## colorizes text when using html or pdf output
## just spits out text x for word
colorize <- function(x, color) {
  if(color=="todo"){
    color <- "red"
    x <- paste0("TODO: ",x)
  }
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{%s}{%s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color, 
      x)
  } else x
}

todo <- function(x){
  paste0("**",colorize(x,"todo"),"**")
}


outf <- "output-02-meta/"
unlink(outf,recursive=TRUE)
dir.create(outf,recursive=TRUE)


source('funcs.R')
library(readxl)
library(ggplot2)
library(kableExtra)
library(latex2exp)
library(DescTools)

## confidence interval alpha
ALPHA <- 0.1
```


## Outline

* Reproduce and extend on results in [Cancer Stage Compared With Mortality as End Points in Randomized Clinical Trials of Cancer Screening A Systematic Review and Meta-Analysis](https://jamanetwork.com/journals/jama/article-abstract/2817338)
    * Data available here: https://github.com/hilaryrobbins/cancer_screening_endpoints
    * Filename: cancer_screening_endpoints_data.xlsx


```{r}
fname <- "data-feng/cancer_screening_endpoints_data.xlsx"
dat <- read_excel(fname)


## clean up intervention names
dat$Intervention
temp <- gsub("1. ","",dat$Intervention,fixed=TRUE)
temp <- gsub("2. ","",temp,fixed=TRUE)
temp <- gsub("Flexible sigmoidoscopy","Sigmoid.",temp,fixed=TRUE)
temp <- gsub("with or without a single FOBT","+/- FOBT",temp,fixed=TRUE)
temp <- gsub("and transvaginal ultrasound","+ TVU",temp,fixed=TRUE)
dat$Intervention_short <- temp


dat$sname <- vapply(strsplit(dat$`Study name`,":",fixed=TRUE),
                        function(x){x[1]},
                        c(NA_character_))
dat$sname <- paste(dat$sname,paste0("(",dat$Intervention_short,")"))
dat$sname <- as.factor(dat$sname)


## compute death reduction
dat$Death_Prop_Arm1 <- dat$Cancer_deaths_arm1/dat$N_arm1
dat$Death_Prop_Arm2 <- dat$Cancer_deaths_arm2/dat$N_arm2
dat$MortalityReduction <- 100*((dat$Death_Prop_Arm1 - dat$Death_Prop_Arm2) / dat$Death_Prop_Arm1)


## compute late stage incidence reduction
dat$LateStage_Prop_Arm1 <- dat$Stage_3_4_arm1/dat$N_arm1
dat$LateStage_Prop_Arm2 <- dat$Stage_3_4_arm2/dat$N_arm2
dat$LateStageReduction <- 100*((dat$LateStage_Prop_Arm1 - dat$LateStage_Prop_Arm2) / dat$LateStage_Prop_Arm1)


## comparison of death between arms
ggplot(dat,aes(x=Death_Prop_Arm1,y=Death_Prop_Arm2)) +
  geom_point() + geom_abline(slope=1,intercept=0)


## comparison of late stage incidence between arms
ggplot(dat,aes(x=LateStage_Prop_Arm1,y=LateStage_Prop_Arm2)) +
  geom_point() + geom_abline(slope=1,intercept=0)


## primary analysis did not include "Alexander et al Br J Can"
subset(dat,Cancer_type=="Breast cancer")
```


### Figure 1A: Breast

```{r}
ggplot(subset(dat,Cancer_type=="Breast cancer" & primary_analysis=="yes"),
       aes(x=LateStageReduction,y=MortalityReduction)) +
  geom_point() + 
  geom_vline(xintercept=0,color='red') + 
  geom_hline(yintercept=0,color='red') +
  coord_cartesian(xlim=c(-50,75),ylim=c(-50,75))
```



### Figure 1B: Colorectal Cancer

```{r}
table(dat$Cancer_type)
colnames(dat)

table(dat$primary_analysis)

ggplot(subset(dat,Cancer_type=="Colorectal cancer" & primary_analysis=="yes"),
       aes(x=LateStageReduction,y=MortalityReduction)) +
  geom_point() + 
  geom_vline(xintercept=0,color='red') + 
  geom_hline(yintercept=0,color='red') +
  coord_cartesian(xlim=c(-50,75),ylim=c(-50,75))


```



## Plots with Uncertainties 


We now make figures with uncertainties. Since we do not know correlation for each study, this will be assumed.








### Figure 1 D Ovarian


```{r}
dat_sub <- subset(dat,Cancer_type=="Ovarian cancer" & primary_analysis=="yes")
```

```{r}
cols <- scales::hue_pal()(nrow(dat_sub))
names(cols) <- as.character(dat_sub$sname)
p1 <- ggplot(dat_sub,aes(x=LateStageReduction,y=MortalityReduction,color=sname)) +
  geom_point() + 
  geom_vline(xintercept=0,color='black') + 
  geom_hline(yintercept=0,color='black') +
  coord_cartesian(xlim=c(-50,75),ylim=c(-50,75)) +
  theme(legend.title=element_blank()) +
  scale_colour_manual(values = cols)  
print(p1)
```



```{r}
rhos <- c(0.1,0.66,0.9)
ps <- vector("list",length(rhos))
ratio_conf <- vector("list",length(rhos))
els_all <- vector("list",length(rhos))
jj <- 1
ii <- 1
for(jj in 1:length(rhos)){
  ps[[jj]] <- p1
  ratio_conf[[jj]] <- data.frame(Study=dat_sub$sname,
                                 CI=rep(NA_character_,nrow(dat_sub)))
  dat_sub$rho <- rhos[jj]
  vname <- c("LateStage_Prop_Arm1","LateStage_Prop_Arm2",
             "Death_Prop_Arm1","Death_Prop_Arm2","rho")
  els <- list()
  for(ii in 1:nrow(dat_sub)){
    print(ii)
    pp <- as.numeric(dat_sub[ii,vname])
    cent <- (c(dat_sub$LateStageReduction[ii],dat_sub$MortalityReduction[ii]))/100
    n <- dat_sub$N_arm1[ii]
    m <- dat_sub$N_arm2[ii]
    els[[ii]] <- cbind(100*CreateEllipse(pp,cent,n,m,alpha=ALPHA,marginal=TRUE),
                       sname=dat_sub$sname[ii],rho=paste0("rho=",rhos[jj]))
    gCov <- ConstructCovSMMargin(pp,n,m)
    temp <- gCov[1,1]
    gCov[1,1] <- gCov[2,2]
    gCov[2,2] <- temp
    ratio_conf[[jj]][ii,2] <- FiellerCI(cent[2],cent[1],gCov,alpha=ALPHA)$latex
    ##FiellerCI(cent[2],cent[1],gCov,alpha=ALPHA)$latex
  }
  els_all[[jj]] <- do.call(rbind,els)
}
els_all <- do.call(rbind,els_all)
ratio_conf
```




```{r}

dat_sub_rep <- do.call(rbind,replicate(length(rhos),dat_sub,simplify=FALSE))
dat_sub_rep$rho <- paste0("rho=",rep(rhos,each=nrow(dat_sub)))


cols <- scales::hue_pal()(nrow(dat_sub))
names(cols) <- as.character(dat_sub$sname)

dat_sub_rep$rho <- factor(dat_sub_rep$rho)
dat_sub_rep$rho
levels(dat_sub_rep$rho) <- c("rho=0.1"=TeX("$\\rho=0.1$"),"rho=0.66"=TeX("$\\rho=0.66$"),"rho=0.9"=TeX("$\\rho=0.9$"))
dat_sub_rep$rho
els_all$rho <- factor(els_all$rho)
levels(els_all$rho) <- c("rho=0.1"=TeX("$\\rho=0.1$"),"rho=0.66"=TeX("$\\rho=0.66$"),"rho=0.9"=TeX("$\\rho=0.9$"))

p1 <- ggplot(dat_sub_rep,aes(x=LateStageReduction,y=MortalityReduction,color=sname)) +
  geom_point() + 
  geom_vline(xintercept=0,color='black') + 
  geom_hline(yintercept=0,color='black') +
  coord_cartesian(xlim=c(-50,75),ylim=c(-50,75)) +
  theme(legend.title=element_blank()) +
  scale_colour_manual(values = cols)  +
  facet_grid(cols=vars(rho),labeller=label_parsed) +
  geom_path(data=els_all,mapping=aes(x=x,y=y,color=sname)) +
  xlab("Estimated Late-Stage Incidence Reduction") +
  ylab("Estimated Mortality Reduction") +
  theme_bw() +
  theme(legend.title=element_blank())
print(p1)
ggsave(paste0(outf,"ovarian_ellipses.pdf"),width=10,height=2.75)
```




```{r}
temp <- data.frame(ratio_conf[[1]][,1],
                   paste0(dat_sub$N_arm1,"/",dat_sub$N_arm2),
                   dat_sub$`Follow-up, years`,                   
                   round(dat_sub$LateStageReduction),
                   round(dat_sub$MortalityReduction))

colnames(temp) <- c("Study","n (Arm 1/Arm2)","Follow-up (yr)",
                    "$\\widehat{S}$","$\\widehat{M}$")


#colnames(temp) <- c("Study","n (Arm 1/Arm2)","Follow-up (yr)",paste0("$\\rho=",rhos,"$"))
temp

caption <- "Ovarian Screening trials.  \\label{tab:ovarian_rj}"
tab <- kbl(temp,booktabs=TRUE,format="latex",escape=FALSE,caption=caption)
tab


```



```{r}
save_kable(tab,file=paste0(outf,"ovarian.tex"))
```





### Figure 1 B: Colorectal Cancer




```{r}
dat_sub <- subset(dat,Cancer_type=="Colorectal cancer" & primary_analysis=="yes")
```

```{r}
cols <- scales::hue_pal()(nrow(dat_sub))
names(cols) <- as.character(dat_sub$sname)
p1 <- ggplot(dat_sub,aes(x=LateStageReduction,y=MortalityReduction,color=sname)) +
  geom_point() + 
  geom_vline(xintercept=0,color='black') + 
  geom_hline(yintercept=0,color='black') +
  coord_cartesian(xlim=c(-50,75),ylim=c(-50,75)) +
  theme(legend.title=element_blank()) +
  scale_colour_manual(values = cols)  
print(p1)
```




```{r}
rhos <- c(0.1,0.66,0.9)
ps <- vector("list",length(rhos))
ratio_conf <- vector("list",length(rhos))
els_all <- vector("list",length(rhos))
gCovs <- vector("list",length(rhos))
hl <- NULL ## store trials which are sig diff from 0
for(jj in 1:length(rhos)){
  ps[[jj]] <- p1
  gCovs[[jj]] <- vector("list",nrow(dat_sub))  
  ratio_conf[[jj]] <- data.frame(Study=dat_sub$sname,
                                 CI=rep(NA_character_,nrow(dat_sub)))
  dat_sub$rho <- rhos[jj]
  vname <- c("LateStage_Prop_Arm1","LateStage_Prop_Arm2",
             "Death_Prop_Arm1","Death_Prop_Arm2","rho")
  els <- list()
  for(ii in 1:nrow(dat_sub)){
    print(ii)
    pp <- as.numeric(dat_sub[ii,vname])
    cent <- (c(dat_sub$LateStageReduction[ii],dat_sub$MortalityReduction[ii]))/100
    n <- dat_sub$N_arm1[ii]
    m <- dat_sub$N_arm2[ii]
    el <- 100*CreateEllipse(pp,cent,n,m,alpha=ALPHA,marginal=TRUE)
    if((min(el[,1]) > 0 | max(el[,1]) < 0) & (min(el[,2]) > 0 | max(el[,2]) < 0)){
      hl <- c(hl,as.character(dat_sub$sname[ii]))
    }
    els[[ii]] <- cbind(el,
                       sname=dat_sub$sname[ii],rho=paste0("rho=",rhos[jj]))
    gCovs[[jj]][[ii]] <- ConstructCovSMMargin(pp,n,m)
    gCov <- gCovs[[jj]][[ii]]
    ## reverse order of S and M variances
    temp <- gCov[1,1]
    gCov[1,1] <- gCov[2,2]
    gCov[2,2] <- temp
    ratio_conf[[jj]][ii,2:3] <- FiellerCI(cent[2],cent[1],gCov,alpha=ALPHA)$latex
  }
  els_all[[jj]] <- do.call(rbind,els)
}
els_all <- do.call(rbind,els_all)
ratio_conf
```



```{r}
unique(hl)
```




```{r}
length(els_all)
names(els_all)

#BB <- c("MCCCS (Annual FOBT)","PLCO (Sigmoid.)","FOBSFCS (FOBT)","NCCST (FOBT)")
BB <- hl
dat_sub$alpha <- 0.5
dat_sub$alpha[dat_sub$sname %in% BB] <- 1
```




```{r}

dat_sub_rep <- do.call(rbind,replicate(length(rhos),dat_sub,simplify=FALSE))
dat_sub_rep$rho <- paste0("rho=",rep(rhos,each=nrow(dat_sub)))


cols <- scales::hue_pal()(nrow(dat_sub))
names(cols) <- as.character(dat_sub$sname)

dat_sub_rep$rho <- factor(dat_sub_rep$rho)
dat_sub_rep$rho
levels(dat_sub_rep$rho) <- c("rho=0.1"=TeX("$\\rho=0.1$"),"rho=0.66"=TeX("$\\rho=0.66$"),"rho=0.9"=TeX("$\\rho=0.9$"))
dat_sub_rep$rho
els_all$rho <- factor(els_all$rho)
levels(els_all$rho) <- c("rho=0.1"=TeX("$\\rho=0.1$"),"rho=0.66"=TeX("$\\rho=0.66$"),"rho=0.9"=TeX("$\\rho=0.9$"))


els_all$alpha <- 0.3
els_all$alpha[els_all$sname %in% BB] <- 1


temp <- els_all[,c("sname","alpha")]
temp <- temp[!duplicated(temp),]
leg_alpha <- temp[order(as.character(temp[,1,drop=TRUE])),]$alpha

p1 <- ggplot(dat_sub_rep,aes(x=LateStageReduction,y=MortalityReduction,color=sname)) +
  geom_point(aes(alpha=alpha)) +
  geom_vline(xintercept=0,color='black') + 
  geom_hline(yintercept=0,color='black') +
  coord_cartesian(xlim=c(-50,75),ylim=c(-50,75)) +
  theme(legend.title=element_blank()) +
  scale_colour_manual(values = cols)  +
  facet_grid(cols=vars(rho),labeller=label_parsed) +
  geom_path(data=els_all,mapping=aes(x=x,y=y,color=sname,alpha=alpha)) +
  xlab("Estimated Late-Stage Incidence Reduction") +
  ylab("Estimated Mortality Reduction") +
  theme_bw() +
  theme(legend.title=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  guides(colour = guide_legend(override.aes = list(alpha=leg_alpha)),alpha="none")
print(p1)
ggsave(paste0(outf,"colorectal_ellipses.pdf"),width=10,height=2.75)
```




```{r}
temp <- list()
for(ii in 1:length(ratio_conf)){
  temp[[ii]] <- ratio_conf[[ii]][,2]
}
temp <- as.data.frame(temp)

temp <- data.frame(ratio_conf[[1]][,1],
                   paste0(dat_sub$N_arm1,"/",dat_sub$N_arm2),
                   dat_sub$`Follow-up, years`,                   
                   round(dat_sub$LateStageReduction),
                   round(dat_sub$MortalityReduction),
                   round(dat_sub$MortalityReduction/dat_sub$LateStageReduction,1),
                   temp)

colnames(temp) <- c("Study","n (Arm 1/Arm2)","Follow-up (yr)",
                    "$\\widehat{S}$","$\\widehat{M}$","$\\widehat{r}$",paste0("$\\rho=",rhos,"$"))
#temp
#colnames(temp) <- c("Study","n (Arm 1/Arm2)","Follow-up (yr)",paste0("$\\rho=",rhos,"$"))
temp

caption <- "Colorectal Screening trials.  \\label{tab:ovarian_rj}"
header <- data.frame(c(" ",paste0(100*(1-ALPHA),"% CI for r")),
                     c(6,3))
tab <- kbl(temp,booktabs=TRUE,format="latex",escape=FALSE,caption=caption) %>%
    add_header_above(header)
tab
```


```{r}
save_kable(tab,file=paste0(outf,"colorectal_rj.tex"))
```







#### Check Some Results

```{r}
dat_sub
dat_sub[dat_sub$sname=="NCCST (FOBT)",
        c("sname","N_arm1","N_arm2","Cancer_deaths_arm1","Cancer_deaths_arm2")]

ix <- dat_sub$sname=="NCCST (FOBT)"
narm1 <- dat_sub[ix,"N_arm1",drop=TRUE]
narm2 <- dat_sub[ix,"N_arm2",drop=TRUE]
darm1 <- dat_sub[ix,"Cancer_deaths_arm1",drop=TRUE]
darm2 <- dat_sub[ix,"Cancer_deaths_arm2",drop=TRUE]


dd <- matrix(c(narm1-darm1,darm1,narm2-darm2,darm2),byrow=TRUE,nrow=2)
fisher.test(x=dd)

dd <- matrix(c(darm2,darm1,narm2-darm2,narm1-darm1),nrow=2)
dd
RelRisk(dd,conf.level=0.95)
```


```{r}
ix <- which(dat_sub$sname=="NCCST (FOBT)")
ix


pest <- (darm1/narm1 - darm2/narm2)/(darm1/narm1)

varM <- gCovs[[1]][[ix]][2,2]
varM
gCovs[[2]][[ix]]

pest
1-c(pest + 2*sqrt(varM),pest - 2*sqrt(varM))

```




```{r}
BB <- c("NCCST (FOBT)")
els_all$alpha <- 0.2
els_all$alpha[els_all$sname %in% BB] <- 1

dat_sub_rep$alpha <- 0.2
dat_sub_rep$alpha[dat_sub_rep$sname %in% BB] <- 1

temp <- dat_sub_rep[,c("sname","alpha")]
temp <- temp[!duplicated(temp),]
leg_alpha <- temp[order(as.character(temp[,1,drop=TRUE])),]$alpha

p1 <- ggplot(dat_sub_rep,aes(x=LateStageReduction,y=MortalityReduction,color=sname)) +
  geom_point(aes(alpha=alpha)) +
  geom_vline(xintercept=0,color='black') + 
  geom_hline(yintercept=0,color='black') +
  coord_cartesian(xlim=c(-50,75),ylim=c(-50,75)) +
  theme(legend.title=element_blank()) +
  scale_colour_manual(values = cols)  +
  facet_grid(cols=vars(rho),labeller=label_parsed) +
  geom_path(data=els_all,mapping=aes(x=x,y=y,color=sname,alpha=alpha)) +
  xlab("Estimated Late-Stage Incidence Reduction") +
  ylab("Estimated Mortality Reduction") +
  theme_bw() +
  theme(legend.title=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  guides(colour = guide_legend(override.aes = list(alpha=leg_alpha)),alpha="none")
print(p1)
ggsave(paste0(outf,"colorectal_ellipses_nccst.pdf"),width=10,height=2.75)
```




PLCO colorectal and MCCCS (Annual FOBT) colorectal provide most informative results.




### Figure 1 C: Lung Cancer











```{r}
table(dat$Cancer_type)
dat_sub <- subset(dat,Cancer_type=="Lung cancer" & primary_analysis=="yes")
dim(dat_sub)
```

```{r}
cols <- scales::hue_pal()(nrow(dat_sub))
names(cols) <- as.character(dat_sub$sname)
p1 <- ggplot(dat_sub,aes(x=LateStageReduction,y=MortalityReduction,color=sname)) +
  geom_point() + 
  geom_vline(xintercept=0,color='black') + 
  geom_hline(yintercept=0,color='black') +
  coord_cartesian(xlim=c(-50,75),ylim=c(-50,75)) +
  theme(legend.title=element_blank()) +
  scale_colour_manual(values = cols)  
print(p1)
```




```{r}
rhos <- c(0.1,0.66,0.9)
ps <- vector("list",length(rhos))
ratio_conf <- vector("list",length(rhos))
els_all <- vector("list",length(rhos))
gCovs <- vector("list",length(rhos))
hl <- NULL ## store trials which are sig diff from 0
for(jj in 1:length(rhos)){
  ps[[jj]] <- p1
  gCovs[[jj]] <- vector("list",nrow(dat_sub))  
  ratio_conf[[jj]] <- data.frame(Study=dat_sub$sname,
                                 CI=rep(NA_character_,nrow(dat_sub)))
  dat_sub$rho <- rhos[jj]
  vname <- c("LateStage_Prop_Arm1","LateStage_Prop_Arm2",
             "Death_Prop_Arm1","Death_Prop_Arm2","rho")
  els <- list()
  for(ii in 1:nrow(dat_sub)){
    print(ii)
    pp <- as.numeric(dat_sub[ii,vname])
    cent <- (c(dat_sub$LateStageReduction[ii],dat_sub$MortalityReduction[ii]))/100
    n <- dat_sub$N_arm1[ii]
    m <- dat_sub$N_arm2[ii]
    el <- 100*CreateEllipse(pp,cent,n,m,alpha=ALPHA,marginal=TRUE)
    if((min(el[,1]) > 0 | max(el[,1]) < 0) & (min(el[,2]) > 0 | max(el[,2]) < 0)){
      hl <- c(hl,as.character(dat_sub$sname[ii]))
    }
    els[[ii]] <- cbind(el,
                       sname=dat_sub$sname[ii],rho=paste0("rho=",rhos[jj]))
    gCovs[[jj]][[ii]] <- ConstructCovSMMargin(pp,n,m)
    gCov <- gCovs[[jj]][[ii]]
    ## reverse order of S and M variances
    temp <- gCov[1,1]
    gCov[1,1] <- gCov[2,2]
    gCov[2,2] <- temp
    ratio_conf[[jj]][ii,2:3] <- FiellerCI(cent[2],cent[1],gCov,alpha=ALPHA)$latex
  }
  els_all[[jj]] <- do.call(rbind,els)
}
els_all <- do.call(rbind,els_all)
ratio_conf
```




```{r}
length(els_all)
names(els_all)


#BB <- c("MCCCS (Annual FOBT)","PLCO (Sigmoid.)","FOBSFCS (FOBT)","NCCST (FOBT)")
BB <- hl
dat_sub$alpha <- 0.5
dat_sub$alpha[dat_sub$sname %in% BB] <- 1
```




```{r}

dat_sub_rep <- do.call(rbind,replicate(length(rhos),dat_sub,simplify=FALSE))
dat_sub_rep$rho <- paste0("rho=",rep(rhos,each=nrow(dat_sub)))


cols <- scales::hue_pal()(nrow(dat_sub))
names(cols) <- as.character(dat_sub$sname)

dat_sub_rep$rho <- factor(dat_sub_rep$rho)
dat_sub_rep$rho
levels(dat_sub_rep$rho) <- c("rho=0.1"=TeX("$\\rho=0.1$"),"rho=0.66"=TeX("$\\rho=0.66$"),"rho=0.9"=TeX("$\\rho=0.9$"))
dat_sub_rep$rho
els_all$rho <- factor(els_all$rho)
levels(els_all$rho) <- c("rho=0.1"=TeX("$\\rho=0.1$"),"rho=0.66"=TeX("$\\rho=0.66$"),"rho=0.9"=TeX("$\\rho=0.9$"))


els_all$alpha <- 0.3
els_all$alpha[els_all$sname %in% BB] <- 1


temp <- els_all[,c("sname","alpha")]
temp <- temp[!duplicated(temp),]
leg_alpha <- temp[order(as.character(temp[,1,drop=TRUE])),]$alpha

p1 <- ggplot(dat_sub_rep,aes(x=LateStageReduction,y=MortalityReduction,color=sname)) +
  geom_point(aes(alpha=alpha)) +
  geom_vline(xintercept=0,color='black') + 
  geom_hline(yintercept=0,color='black') +
  coord_cartesian(xlim=c(-50,75),ylim=c(-50,75)) +
  theme(legend.title=element_blank()) +
  scale_colour_manual(values = cols)  +
  facet_grid(cols=vars(rho),labeller=label_parsed) +
  geom_path(data=els_all,mapping=aes(x=x,y=y,color=sname,alpha=alpha)) +
  xlab("Estimated Late-Stage Incidence Reduction") +
  ylab("Estimated Mortality Reduction") +
  theme_bw() +
  theme(legend.title=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  guides(colour = guide_legend(override.aes = list(alpha=leg_alpha)),alpha="none")
print(p1)
ggsave(paste0(outf,"lung_ellipses.pdf"),width=10,height=2.75)
```




```{r}
temp <- list()
for(ii in 1:length(ratio_conf)){
  temp[[ii]] <- ratio_conf[[ii]][,2]
}
temp <- as.data.frame(temp)

temp <- data.frame(ratio_conf[[1]][,1],
                   paste0(dat_sub$N_arm1,"/",dat_sub$N_arm2),
                   dat_sub$`Follow-up, years`,                   
                   round(dat_sub$LateStageReduction),
                   round(dat_sub$MortalityReduction),
                   round(dat_sub$MortalityReduction/dat_sub$LateStageReduction,1),
                   temp)

colnames(temp) <- c("Study","n (Arm 1/Arm2)","Follow-up (yr)",
                    "$\\widehat{S}$","$\\widehat{M}$","$\\widehat{r}$",
                    paste0("$\\rho=",rhos,"$"))
#temp
#colnames(temp) <- c("Study","n (Arm 1/Arm2)","Follow-up (yr)",paste0("$\\rho=",rhos,"$"))
temp

caption <- "Colorectal Screening trials.  \\label{tab:ovarian_rj}"
header <- data.frame(c(" ",paste0(100*(1-ALPHA),"% CI for r")),
                     c(6,3))
tab <- kbl(temp,booktabs=TRUE,format="latex",escape=FALSE,caption=caption) %>%
    add_header_above(header)
tab
```


```{r}
save_kable(tab,file=paste0(outf,"lung_rj.tex"))
```








